---
title: "Reproducible templates"
subtitle: "Final project"
author: "Guillermo L. Florez-Montero, M.Sc."
date: "09/11/2020"
output:
  ioslides_presentation:
        widescreen: true
        logo: images/Rlogo.png
        css: style.css
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
```



## About the course

This is the final project of the Coursera course [Reproducible templates for analysis and dissemiation](https://www.coursera.org/learn/reproducible-templates-analysis/). Here I will show some of the skills that I have developed during the course.


## About the course

This is the final project of the Coursera course [Reproducible templates for analysis and dissemiation](https://www.coursera.org/learn/reproducible-templates-analysis/). Here I will show some of the skills that I have developed during the course.


I am particularly excited because thanks to the course, I started preparing all my reports in R Markdown.


## Skills 

**To produce pdf and html documents**

- Customize the text and headers, bold, italics, etc
- Work with templates
- Enter plots, tables, code chunks and images
- Keep a workflow with version control using git and github
- Manage references and bibliography styles

## A plot of the `pressure` dataset

I have used the ggplot system to create a plot

```{r pressure}
ggplot2::ggplot(data = pressure, aes(x = temperature, y = pressure)) + 
      geom_line(colour = "#003333", size = 1.5) +
      theme_bw() +
      labs(y = "Pressure", x = "Temperature") +
      theme(panel.grid = element_blank(),
            axis.title = element_text(size = 14, colour = "black", 
                                      face = "bold"))
```

## A table

This is an example of a table made with the `knitr::kable()` function

<div align="center">
```{r cars}
knitr::kable(head(cars), format = "html", col.names = c("SPEED", "DISTANCE"), align = "c")
```
</div>

## Some tools

Mani of the customizations of this presentations were made using a css style document. For example:

```
slides > slide.title-slide hgroup h1 {
    color: #003333;
}

slides > slide.title-slide p {
  color: #1f2023;
}

slides > slide.title-slide hgroup h2 {
  color: #1f2023;
}

```

I have used this code to change the colors of the title, subtitle and text of the first slide.


## Source

Thank you very much!

I really recommend to take the Course of Reproducible templates.

If you want to see the codes to generate this presentation, please visit my [github page](https://github.com/gflorezm/FinalProject).

